\documentclass[letterpaper]{article}
\usepackage[margin=1in]{geometry}

\usepackage[mediumspace,mediumqspace,squaren,textstyle]{SIunits}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage [autostyle, english = american]{csquotes}
\MakeOuterQuote{"}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{helvet}

\title{Qubit Quantification of DNA}

\author{Eisen Lab}

\date{April 4, 2014}

\begin{document}
\maketitle


\section{Introduction}

The protocol uses a Qubit Fluorometer (Invitrogen) to quantify DNA, e.g. from environmental DNA extractions or purfied PCR products. The Qubit kit is stored at 4$^{\circ}$C (Quant-iT dsDNA Assay Kit, High Sensitivity, 1000 assays. Invitrogen product no. Q33120).

\section{Protocol}

\subsection{Prepare working solution}

Prepare a master mix of working solution by diluting Florescent Dye (Quant-iT dsDNA HS reagent) to Quant-iT dsDNA HS buffer at a final ratio of (1:199): add \unit{1}{\micro\litre} of dye into every \unit{198}{\micro\litre} of Qubit buffer. Ensure that all solutions are fully liquid before mixing; the Florescent Dye may crystallize during storage at 4$^{\circ}$C.


\subsection{Calibrate Qubit}

Before quantifying DNA, the Qubit machine should be calibrated using standard solutions. However, if the machine has been recently calibrated, select "use last calibration" when prompted on screen.

\subsection{Prepare DNA samples}

Prepare sample solution by adding \unit{1-10}{\micro\litre} of each DNA sample to working solution (\unit{190-199}{\micro\litre}, respectively). Each sample should be prepared in a separate \unit{0.3}{\milli\litre} Qubit tube (Qubit assay tubes, Invitrogen product no. Q32856), where the final volume of the prepared sample solution is \unit{200}{\micro\litre} (DNA sample mixed with working solution).

\subsection{Measure Sample Concentration}

Measure the DNA concentration of each sample, as follows:

\begin{itemize}
\item On the Qubit screen prompt, chose "Quant-it dsDNA, HS" (high sensitivity DNA quantification)
\item Choose "use last calibration"
\item Insert sample into slot, close plastic cover, and press "GO" button
\item Select "calculate the sample concentration" and then choose the input sample volume used in Step 2.3
\item If the Qubit cannot quantify DNA ("sample concentration too low"), prepare a new sample solution by increasing the amount of DNA diluted into the working solution (Step 2.3, for example, use \unit{5}{\micro\litre} instead of \unit{1}{\micro\litre} of your DNA sample). Re-measure new sample solution.
\end{itemize}



\end{document}